Clinician Scheduler Documentation

### 2019-07-09 docs/build/latex/ClinicianScheduler.tex
Update Latex version of manual

\title{Clinician Scheduler Documentation}
\date{Jul 08, 2019}
\release{1.0}
\author{David Landsman}
\newcommand{\sphinxlogo}{\vbox{}}
\renewcommand{\releasename}{Release}
\makeindex

@@

\begin{sphinxShadowBox}
\sphinxstyletopictitle{Table of Contents}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{manual:id5}}{\hyperref[\detokenize{manual:clinician-configuration}]{\sphinxcrossref{Clinician Configuration}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{manual:id6}}{\hyperref[\detokenize{manual:creating-a-new-configuration-file}]{\sphinxcrossref{Creating a new configuration file}}}

\item {} 
\phantomsection\label{\detokenize{manual:id7}}{\hyperref[\detokenize{manual:saving-the-configuration-file}]{\sphinxcrossref{Saving the configuration file}}}

\item {} 
\phantomsection\label{\detokenize{manual:id8}}{\hyperref[\detokenize{manual:loading-a-configuration-file}]{\sphinxcrossref{Loading a configuration file}}}

\item {} 
\phantomsection\label{\detokenize{manual:id9}}{\hyperref[\detokenize{manual:adding-a-new-clinician}]{\sphinxcrossref{Adding a new clinician}}}

\item {} 
\phantomsection\label{\detokenize{manual:id10}}{\hyperref[\detokenize{manual:deleting-an-existing-clinician}]{\sphinxcrossref{Deleting an existing clinician}}}

\item {} 
\phantomsection\label{\detokenize{manual:id11}}{\hyperref[\detokenize{manual:editing-an-existing-clinician}]{\sphinxcrossref{Editing an existing clinician}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{manual:id12}}{\hyperref[\detokenize{manual:scheduling}]{\sphinxcrossref{Scheduling}}}

@@

\item {} 
\phantomsection\label{\detokenize{manual:id13}}{\hyperref[\detokenize{manual:generating-a-schedule}]{\sphinxcrossref{Generating a schedule}}}

\item {} 
\phantomsection\label{\detokenize{manual:id14}}{\hyperref[\detokenize{manual:exporting-a-schedule}]{\sphinxcrossref{Exporting a schedule}}}

\item {} 
\phantomsection\label{\detokenize{manual:id15}}{\hyperref[\detokenize{manual:publishing-a-schedule-to-google-calendar}]{\sphinxcrossref{Publishing a schedule to Google Calendar}}}

\item {} 
\phantomsection\label{\detokenize{manual:id16}}{\hyperref[\detokenize{manual:clearing-a-published-schedule}]{\sphinxcrossref{Clearing a published schedule}}}

@@

\item {} 
\phantomsection\label{\detokenize{manual:id17}}{\hyperref[\detokenize{manual:sample-output}]{\sphinxcrossref{Sample Output}}}

@@

\chapter{Clinician Configuration}
\label{\detokenize{manual:clinician-configuration}}\label{\detokenize{manual:id1}}
Before we can generate a schedule, we need to create a configuration file
that specifies which clinicians are available, and how many weeks each
clinician should fulfill.

@@

\begin{sphinxadmonition}{warning}{Warning:}
Unsaved changes to a configuration file will be discarded upon clicking
\sphinxtitleref{New Config}.
\end{sphinxadmonition}

@@

\section{Loading a configuration file}
\label{\detokenize{manual:loading-a-configuration-file}}
If you would like to open a previously created configuration file, simply
click on \sphinxtitleref{Open Config}, navigate to the location of the configuration file,
and select it.

@@

\section{Adding a new clinician}
\label{\detokenize{manual:adding-a-new-clinician}}\label{\detokenize{manual:id2}}
1. From the configuration tab, click \sphinxtitleref{New Clinician}. You should see a
form for supplying details.

@@

\subsection{Scheduling}
\label{\detokenize{manual:scheduling}}

\section{Generating a schedule}
\label{\detokenize{manual:generating-a-schedule}}\label{\detokenize{manual:id3}}
Once you have created a configuration file, you can switch over to the
\sphinxtitleref{Scheduler} tab of the application in order to generate a schedule.
\begin{enumerate}
\item {} 
From the scheduling tab, click on \sphinxtitleref{Load} and select the configuration
file that you generated in {\hyperref[\detokenize{manual:clinician-configuration}]{\sphinxcrossref{\DUrole{std,std-ref}{Clinician Configuration}}}}

@@

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/generate\_schedule/step1\_load\_config.png}{\sphinxincludegraphics{{step1_load_config}.png}}\end{figure}
\begin{enumerate}
\setcounter{enumi}{1}
\item {} 
Enter the calendar year for the schedule that you want to generate.

@@

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/generate\_schedule/step2\_calendar\_year.png}{\sphinxincludegraphics{{step2_calendar_year}.png}}\end{figure}
\begin{enumerate}
\setcounter{enumi}{2}
\item {} 
\sphinxstylestrong{(Optional)} In order to retrieve the time-off requests that were populated
in Google calendar in \DUrole{xref,std,std-ref}{adding-clinician-requests}, we need to specify the
calendar ID. Open the calendar in your browser, and navigate to the
\sphinxtitleref{Settings and sharing} page.
On the setting page, navigate to the \sphinxtitleref{Integrate calendar} section, and copy
the value under \sphinxtitleref{Calendar ID} to your clipboard.
Paste this value into the \sphinxtitleref{Google Calendar ID} textbox on the \sphinxtitleref{Scheduler}
tab.

@@

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/generate\_schedule/step3\_calendar\_id.png}{\sphinxincludegraphics{{step3_calendar_id}.png}}\end{figure}
\begin{enumerate}
\setcounter{enumi}{3}
\item {} 
\sphinxstylestrong{(Optional)} If you supplied a calendar ID in step 3, you can configure
the options \sphinxtitleref{Retrieve Time-off Requests} and \sphinxtitleref{Retrieve Long Weekends} as necessary.
Enabling \sphinxtitleref{Retrieve Time-off Requests} will read the time-off calendar events
from the calendar specified in \sphinxtitleref{Calendar ID}, while enabling
\sphinxtitleref{Retrieve Long Weekends} will read the holiday events from that calendar.

@@

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/generate\_schedule/step4\_retrieve\_events.png}{\sphinxincludegraphics{{step4_retrieve_events}.png}}\end{figure}
\begin{enumerate}
\setcounter{enumi}{4}
\item {} 
\sphinxstylestrong{(Optional)} In the case that you only need to generate a schedule for
a subset of the calendar year, you can select the amount of blocks you need
to generate by specifying a value in \sphinxtitleref{Number of Blocks}. By default, the
scheduler will generate a full schedule, corresponding to 26 blocks.

@@

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/generate\_schedule/step5\_number\_of\_blocks.png}{\sphinxincludegraphics{{step5_number_of_blocks}.png}}\end{figure}
\begin{enumerate}
\setcounter{enumi}{5}
\item {} 
Click on \sphinxtitleref{Generate}, and after a few moments you should see a preview of
the generated schedule in the table.

\sphinxstylestrong{(Optional)} See \DUrole{xref,std,std-ref}{authentication} in case you encounter problems
with Google calendar at this stage.

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/generate\_schedule/step6\_generate\_schedule.png}{\sphinxincludegraphics{{step6_generate_schedule}.png}}\end{figure}

\begin{sphinxadmonition}{note}{Note:}
It is possible that the scheduler will not be able to come up with a
schedule that satisfies your constraints. You can try adjusting
some constraints by changing the minimum and maximum number of blocks of
clinicians in the configuration file. See {\hyperref[\detokenize{manual:clinician-configuration}]{\sphinxcrossref{\DUrole{std,std-ref}{Clinician Configuration}}}}
for more information on changing the configuration file.
\end{sphinxadmonition}

\section{Exporting a schedule}
\label{\detokenize{manual:exporting-a-schedule}}
If you are satisfied with the generated schedule, you can choose to export
it as an Excel file. There are two format options: \sphinxtitleref{Yearly Export} and
\sphinxtitleref{Monthly Export}.

@@

\section{Publishing a schedule to Google Calendar}
\label{\detokenize{manual:publishing-a-schedule-to-google-calendar}}\label{\detokenize{manual:id4}}
If you are satisfied with the generated schedule, you can publish it
to Google calendar, by clicking on \sphinxtitleref{Publish}.

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/publish\_schedule/publish\_schedule.png}{\sphinxincludegraphics{{publish_schedule}.png}}\end{figure}

\begin{sphinxadmonition}{warning}{Warning:}
This process might take some time, especially if the number of events
to be published is quite large.
\end{sphinxadmonition}

\section{Clearing a published schedule}
\label{\detokenize{manual:clearing-a-published-schedule}}
If you want to remove all the published events created by the application,
simply click on \sphinxtitleref{Clear}.

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/publish\_schedule/clear\_schedule.png}{\sphinxincludegraphics{{clear_schedule}.png}}\end{figure}

\begin{sphinxadmonition}{warning}{Warning:}
This process might take some time, especially if the number of published
events is quite large.
\end{sphinxadmonition}

\chapter{Sample Output}
\label{\detokenize{manual:sample-output}}
Yearly output format

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/sample\_yearly.png}{\sphinxincludegraphics{{sample_yearly}.png}}\end{figure}

Monthly output format

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/sample\_monthly.png}{\sphinxincludegraphics{{sample_monthly}.png}}\end{figure}

>>>>

\title{Clinician Scheduler Documentation}
\date{Jul 09, 2019}
\release{2.0}
\author{David Landsman}
\newcommand{\sphinxlogo}{\vbox{}}
\renewcommand{\releasename}{Release}
\makeindex

@@

\begin{sphinxShadowBox}
\sphinxstyletopictitle{Table of Contents}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{manual:id4}}{\hyperref[\detokenize{manual:clinician-configuration}]{\sphinxcrossref{Clinician Configuration}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{manual:id5}}{\hyperref[\detokenize{manual:creating-a-new-configuration-file}]{\sphinxcrossref{Creating a new configuration file}}}

\item {} 
\phantomsection\label{\detokenize{manual:id6}}{\hyperref[\detokenize{manual:saving-the-configuration-file}]{\sphinxcrossref{Saving the configuration file}}}

\item {} 
\phantomsection\label{\detokenize{manual:id7}}{\hyperref[\detokenize{manual:loading-a-configuration-file}]{\sphinxcrossref{Loading a configuration file}}}

\item {} 
\phantomsection\label{\detokenize{manual:id8}}{\hyperref[\detokenize{manual:adding-a-new-clinician}]{\sphinxcrossref{Adding a new clinician}}}

\item {} 
\phantomsection\label{\detokenize{manual:id9}}{\hyperref[\detokenize{manual:deleting-an-existing-clinician}]{\sphinxcrossref{Deleting an existing clinician}}}

\item {} 
\phantomsection\label{\detokenize{manual:id10}}{\hyperref[\detokenize{manual:editing-an-existing-clinician}]{\sphinxcrossref{Editing an existing clinician}}}

@@

\item {} 
\phantomsection\label{\detokenize{manual:id11}}{\hyperref[\detokenize{manual:requests-holiday-weekends}]{\sphinxcrossref{Requests \& Holiday Weekends}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{manual:id12}}{\hyperref[\detokenize{manual:clinician-requests-excel-file}]{\sphinxcrossref{Clinician Requests Excel File}}}

\item {} 
\phantomsection\label{\detokenize{manual:id13}}{\hyperref[\detokenize{manual:holiday-weekends-excel-file}]{\sphinxcrossref{Holiday Weekends Excel File}}}

@@

\item {} 
\phantomsection\label{\detokenize{manual:id14}}{\hyperref[\detokenize{manual:scheduling}]{\sphinxcrossref{Scheduling}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{manual:id15}}{\hyperref[\detokenize{manual:generating-a-schedule}]{\sphinxcrossref{Generating a schedule}}}

\item {} 
\phantomsection\label{\detokenize{manual:id16}}{\hyperref[\detokenize{manual:exporting-a-schedule}]{\sphinxcrossref{Exporting a schedule}}}

\item {} 
\phantomsection\label{\detokenize{manual:id17}}{\hyperref[\detokenize{manual:sample-output}]{\sphinxcrossref{Sample Output}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{manual:id18}}{\hyperref[\detokenize{manual:yearly-excel-format}]{\sphinxcrossref{Yearly Excel Format}}}

\item {} 
\phantomsection\label{\detokenize{manual:id19}}{\hyperref[\detokenize{manual:monthly-excel-format}]{\sphinxcrossref{Monthly Excel Format}}}

@@

\chapter{Clinician Configuration}
\label{\detokenize{manual:clinician-configuration}}\label{\detokenize{manual:id1}}
The clinician configuration specifies which clinicians are available,
which divisions they are covering, and how many weeks they should cover
in each of their divisions.

@@

\begin{sphinxadmonition}{warning}{Warning:}
Unsaved changes to a configuration file will be discarded upon clicking
on \sphinxtitleref{New Config}.
\end{sphinxadmonition}

@@

\section{Loading a configuration file}
\label{\detokenize{manual:loading-a-configuration-file}}
If you would like to open a previously created configuration file, simply
click on \sphinxtitleref{Open Config}, navigate to the location of the file,
and select it.

@@

\section{Adding a new clinician}
\label{\detokenize{manual:adding-a-new-clinician}}\label{\detokenize{manual:id2}}
1. From the configuration tab, click \sphinxtitleref{New Clinician}. You should see a
form for supplying clinician details.

@@

\chapter{Requests \& Holiday Weekends}
\label{\detokenize{manual:requests-holiday-weekends}}\label{\detokenize{manual:requests-and-holidays}}
Clinician requests for time-off and the dates of holiday weekends are
supplied using a pair of excel files.

\section{Clinician Requests Excel File}
\label{\detokenize{manual:clinician-requests-excel-file}}
The requests file should have a single sheet per clinician that is in the
configuration file you created in {\hyperref[\detokenize{manual:clinician-configuration}]{\sphinxcrossref{\DUrole{std,std-ref}{Clinician Configuration}}}}. Inside
each sheet, each request is entered on a separate row, containing the start
and end date (inclusive) of the request.

\begin{sphinxadmonition}{warning}{Warning:}
Make sure each value in the Excel file is formatted as a date!
\end{sphinxadmonition}

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/requests\_holidays/excel\_requests.png}{\sphinxincludegraphics{{excel_requests}.png}}\end{figure}

\begin{sphinxadmonition}{note}{Note:}
To enter a request for a single day, use the same value for both start
and end date.
\end{sphinxadmonition}

\section{Holiday Weekends Excel File}
\label{\detokenize{manual:holiday-weekends-excel-file}}
The holiday weekends file should have a single sheet with the dates of the
holiday weekends, one in each row.

\begin{sphinxadmonition}{warning}{Warning:}
Make sure each value in the Excel file is formatted as a date!
\end{sphinxadmonition}

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/requests\_holidays/excel\_holidays.png}{\sphinxincludegraphics{{excel_holidays}.png}}\end{figure}

\chapter{Scheduling}
\label{\detokenize{manual:scheduling}}

\section{Generating a schedule}
\label{\detokenize{manual:generating-a-schedule}}\label{\detokenize{manual:id3}}
Once you have created a configuration file, you can switch over to the
\sphinxtitleref{Scheduler} tab of the application in order to generate a schedule.
\begin{enumerate}
\item {} 
Load the configuration, requests, and holidays files that you created
earlier in {\hyperref[\detokenize{manual:clinician-configuration}]{\sphinxcrossref{\DUrole{std,std-ref}{Clinician Configuration}}}} and {\hyperref[\detokenize{manual:requests-and-holidays}]{\sphinxcrossref{\DUrole{std,std-ref}{Requests \& Holiday Weekends}}}}.

@@

\begin{sphinxadmonition}{note}{Note:}
You can be sure that everything loaded correctly by checking the output
on the right.
\end{sphinxadmonition}

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/generate\_schedule/step1\_load.png}{\sphinxincludegraphics{{step1_load}.png}}\end{figure}
\begin{enumerate}
\setcounter{enumi}{1}
\item {} 
Set the starting calendar year for the schedule, as well as the number
of 2-week blocks that you want the schedule to cover. By default, the calendar
year is the upcoming year, and the number of blocks is 26, to cover a full
year.

@@

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/generate\_schedule/step2\_year\_blocks.png}{\sphinxincludegraphics{{step2_year_blocks}.png}}\end{figure}
\begin{enumerate}
\setcounter{enumi}{2}
\item {} 
\sphinxstylestrong{(Optional)} Check the \sphinxtitleref{Shuffle?} checkbox if you would like the scheduler
to generate a slightly different schedule each time you click on \sphinxtitleref{Generate}.

@@

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/generate\_schedule/step3\_optional\_shuffle.png}{\sphinxincludegraphics{{step3_optional_shuffle}.png}}\end{figure}
\begin{enumerate}
\setcounter{enumi}{3}
\item {} 
\sphinxstylestrong{(Optional)} Check the \sphinxtitleref{Verbose Output} checkbox if you would like
to see detailed output on the right after the scheduler finishes generating
the schedule.

@@

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/generate\_schedule/step4\_optional\_verbose.png}{\sphinxincludegraphics{{step4_optional_verbose}.png}}\end{figure}
\begin{enumerate}
\setcounter{enumi}{4}
\item {} 
Click on \sphinxtitleref{Generate} to generate a schedule.

@@

\begin{sphinxadmonition}{warning}{Warning:}
Depending on the amount of clinicians and requests provided, it may take
some time to find an optimal schedule.
\end{sphinxadmonition}

\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/generate\_schedule/step5\_generate.png}{\sphinxincludegraphics{{step5_generate}.png}}\end{figure}

\begin{sphinxadmonition}{warning}{Warning:}
It is possible that the scheduler will not be able to come up with a
schedule that satisfies your constraints. This can be a result of either
of the following reasons:
\begin{itemize}
\item {} 
There are not enough clinicians to distribute evenly throughout the year

\item {} 
The minimum and maximum number of blocks of clinicians are too restrictive

Try changing the configuration file by adding new clinicians, or changing
the min/max blocks of different clinicians to allow for more flexibility.

See {\hyperref[\detokenize{manual:clinician-configuration}]{\sphinxcrossref{\DUrole{std,std-ref}{Clinician Configuration}}}} for more information on modifying the configuration file.
\end{sphinxadmonition}

\section{Exporting a schedule}
\label{\detokenize{manual:exporting-a-schedule}}
If you are satisfied with the generated schedule, you can choose to export
it as an Excel file. There are two Excel format options: \sphinxtitleref{Yearly Export} and
\sphinxtitleref{Monthly Export}.

@@

\chapter{Sample Output}
\label{\detokenize{manual:sample-output}}

\section{Yearly Excel Format}
\label{\detokenize{manual:yearly-excel-format}}
\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/sample\_yearly.png}{\sphinxincludegraphics{{sample_yearly}.png}}\end{figure}

\section{Monthly Excel Format}
\label{\detokenize{manual:monthly-excel-format}}
\begin{figure}[H]
\centering
\sphinxhref{\_static/images/scheduling/sample\_monthly.png}{\sphinxincludegraphics{{sample_monthly}.png}}\end{figure}
